A Domain Specific Language for SpectreGuard

### 2020-12-11 paper/main.tex
done with paper?

This also outlines procedure that the C code generator uses. When code written
in the EDSL is transformed into C code, a name generator first annotates the
abstract syntax tree (AST) with globally unique names (enforcing the Barendregt
variable convention; see Chapter 2 in~\cite{BarendregtConversion}). This
annotated AST can be used by both the code generator and the information flow
leak analysis tool (the latter is described in Section \ref{sec:Analysis}). It
is worth noting that, as a result of this technique, the names in the generated
C code will not generally be the same as the names in the EDSL code.

@@

...

@@

Additionally, features to safely convert between sensitivity levels could prove
useful. A conversion from public to secret would be straightforward. A situational conversion
going the other direction could be provided by an instruction in the EDSL
which might perform a Spectre mitigation measure, such as a cache flush.~\cite{PLtea-james}

@@

Another possible avenue of future work is the creation of ``obfuscate''
operations: operations which change the contents of secret variable in such a
way that it is not feasible to recover the original contents. An example is a
hash function. This could be a mechanism to go from a secret variable to a
public variable. The type system and analysis tool could then be modified to
account for this. Perhaps it is also possible to allow the programmer to create
new obfuscate functions, maybe using a restricted subset of the language. Also,
it might be possible to use information theory concepts, like the conditional
entropy~\cite{InfoTheory} of the function output conditioned on its input, to create a framework
to statically provide assurance that there is a certain limit on how much
information could be theoretically recovered (in general) after such a
programmer-defined obfuscate function is applied.

>>>>

This also outlines procedure that the C code generator uses. When code written
in the EDSL is transformed into C code, a name generator first annotates the
abstract syntax tree (AST) with globally unique names (enforcing the Barendregt
variable convention; see Chapter 2 in~\cite{BarendregtConversion}). This
annotated AST can be used by both the code generator and the information flow
leak analysis tool (the latter is described in Section \ref{sec:Analysis}). The
code generator performs a transformation from code in the syntax given in the
left column of Fig.~\ref{fig:Syntax} to the right column of the figure. This is
transformation recursively applies itself when it reaches the parts marked with
an overline in the right column of the figure. It is worth noting that, as a
result of this technique, the names in the generated C code will not generally
be the same as the names in the EDSL code.

@@

@@

Additionally, features to safely convert between sensitivity levels could prove
useful. A conversion from public to secret would be straightforward. A situational conversion
going the other direction could be provided by an instruction in the EDSL
which might perform a Spectre mitigation measure, such as a cache flushes at appropriate times.~\cite{PLtea-james}

@@

Another possible avenue of future work is the creation of ``obfuscate''
operations: operations which change the contents of secret variable in such a
way that it is not feasible to recover the original contents (within the context
of a certain threat model). An example is a hash function. This could be a
mechanism to go from a secret variable to a public variable. The type system and
analysis tool could then be modified to account for this. Perhaps it is also
possible to allow the programmer to create new obfuscate functions, maybe using
a restricted subset of the language. Also, it might be possible to use
information theory concepts, like the conditional entropy~\cite{InfoTheory} of
the function output conditioned on its input, to create a framework to
statically provide assurance that there is a certain limit on how much
information could be theoretically recovered (in general) after such a
programmer-defined obfuscate function is applied. Perhaps a sub-language for
obfuscate functions could be developed, which allows the expression of such
``information losing'' functions, where a notion of ``information loss'' can
be given by the programmers so that it fits the particular threat model
that they are operating under. Then the implementation of the obfuscate
functions could be statically checked to ensure that they do, in fact,
follow this information loss specification. This might be able to be accomplished
via an extension of the type system, similarly to how the type system is used in~\cite{Lifty}.
